Array Programming with NumPy

### 2020-06-01 methods.tex
Mention lapack history and note it is an external tool
This tries to address gh-72. I expanded the list of functionality
a bit, since it seemed strange to quite as concise if the paragraph
is longer. Hoewver, now the first paragraph might be very concise
since it uses the old style.

NumPy's linear algebra library includes functions for: solving linear
systems of equations; computing various functions of a matrix, including
the determinant, the norm, the inverse, and the pseudo-inverse;
computing the Cholesky, eigenvalue, and singular value decompositions of a matrix;
and more.

@@

A Python \emph{wheel} ({https://www.python.org/dev/peps/pep-0427/})
is a standard file format for distributing Python libraries.
In addition to Python code, a wheel may include compiled
C extensions and other binary data.
This is important, because many libraries, including NumPy,
require a C compiler and other build tools to build the software
from the source code, making it difficult for many users to install
the software on their own.  The introduction of wheels to the Python
packaging system has made it much easier for users to install
precompiled libraries.

>>>>

NumPy's linear algebra library provides an interface to established
linear algebra methods. These include solving linear systems of equations
and computing various matrix properties, such as the determinant,
the norm, the inverse, and the pseudo-inverse.
As well as computing the Cholesky, eigenvalue, and singular value decompositions
of a matrix and further functions.
For best performance and reliability the algorithms are provided by leveraging
an external implemention of the LAPACK interface \cite{LAPACK}.
LAPACK itself was first released in 1992 and is based on the EISPACK and LINPACK
open-source libraries. It is part of Netlib, a repository of
mathematical software, papers and databases and has a long history of open,
community-wide development. \cite{dongarra1990lapack,dongarra2008netlib}

@@

A Python \emph{wheel} (\url{https://www.python.org/dev/peps/pep-0427/})
is a standard file format for distributing Python libraries.
In addition to Python code, a wheel may include compiled
C extensions and other binary data.
This is important, because many libraries, including NumPy,
require a C compiler and other build tools to build the software
from the source code, making it difficult for many users to install
the software on their own.  The introduction of wheels to the Python
packaging system has made it much easier for users to install
precompiled libraries.
